The Numerical Accuracy of Computing Electrostatic Interaction in the Inhomogeneous and Correlated Molecular Systems: for the Ewald Summation, SPME and Staggered Mesh Ewald Methods.

### 2012-07-13 longRange.hetero/alltext/publish/resubmit/lett.tex
everything black, improve letter

In the revised manuscript, all the additions are marked in red, to help the
reviewers to located them immediately in the text.\\

@@

In the revised manuscript,
we consider both of the two types of the correlations:
(1) the bonded correlation
that originates from the rigid H-O
bond and H-O-H angle within one molecule,
and (2) the
non-bonded correlation or the
intermolecular correlation that originates from
a complex coupling of various intermolecular interaction.
Estimates for the bonded correlation
have already been developed by the old manuscript,
while the non-bonded estimate
is newly added according to the reviewers' suggestion.
Please note that
both the bonded and non-bonded nearest neighbor approximations
require some uniformity of the correlation in the system:
the bonded estimate requires the uniformity of the water
direction preference (as has been discussed in the old manuscript),
while the non-bonded estimate requires the uniformity
of the density distribution and the isotropicity of the system.
Otherwise the cost of the error estimate would be $\mathcal O(N^2\log N)$.
For the non-bonded correlation,  the nearest neighbor approximation 
is expressed in terms of the radial distribution
functions (RDFs), see the new Eq. (21) and (22). In example 3, a global RDF is not well defined,
so we calculated the RDF and nearest neighbor approximation
only for the liquid phase, see the dotted line in Fig.7. By adding
the non-bonded correlation, the quality of the error estimate
is further improved.
Also the convergence with respect to
the neighboring range $R_g$ is investigated, see Fig.8.
Relevant changes to the manuscript
have been made on page 9,
11 (4-th line from the bottom), 12, 29 (12-th line). All changes are marked 
in red for convenience.
\\

@@

In the revised manuscript, the correlation error are considered
in two types: 
(1) the bonded correlation
that originates from the rigid H-O
bond and H-O-H angle within one molecule,
and (2) the
non-bonded correlation or the
intermolecular correlation that originates from
a complex coupling of various intermolecular interaction.
Estimates for the bonded correlation
have already been developed by the old manuscript,
while the non-bonded estimate
is newly developed according to the reviewers' suggestion.
Please note that
both the bonded and non-bonded nearest neighbor approximations
require some uniformity of the correlation in the system:
the bonded estimate requires the uniformity of the water
direction preference (as has been discussed in the old manuscript),
while the non-bonded estimate requires the uniformity
of the density distribution and the isotropicity of the system, which
are also the prerequisites for reducing $\rho^{(2)}$ to $g(r)$.
Otherwise the cost of the error estimate would be $\mathcal O(N^2\log N)$.
For the non-bonded correlation,  the nearest neighbor approximation 
is expressed in terms of the radial distribution
functions (RDFs) in the new Eqn. (21) and (22).
In example 3, a global RDF is not well defined
(because the system is inhomogeneous),
so we calculated the RDF and nearest neighbor approximation
only for the liquid phase, see the dotted line in Fig.7. By adding the
non-bonded correlation, the quality of the error estimate
is further improved.
Also the convergence with respect to
the neighboring range $R_g$ (the $r_c$ in the reviewer's comment)
is investigated (Fig.8). 
Relevant changes to the manuscript
have been made on page 9,
11 (4-th line from the bottom), 12, 29 (12-th line). All changes are marked 
in red for convenience.
\\

>>>>

In the revised manuscript, all the major additions are marked in red, to help the
reviewers to located them immediately in the text.\\

@@

In the revised manuscript,
we consider both of the two types of the correlations:
(1) the bonded correlation
that originates from the rigid H-O
bond and H-O-H angle within one molecule,
and (2) the
non-bonded correlation or the
intermolecular correlation that originates from
a complex coupling of various intermolecular interactions.
Estimates for the bonded correlation
have already been developed by the old manuscript,
while the non-bonded estimate
is newly added according to the reviewers' suggestion.
The nearest neighbors are defined by neighbors closer than
a neighboring range $R_g$.
The non-bonded nearest neighbor approximation 
is expressed in terms of the radial distribution
functions (RDFs), see the new Eq. (21) and (22).
Please note that
both the bonded and non-bonded nearest neighbor approximations
require some uniformity of the correlation in the system:
the bonded estimate requires the uniformity of the water
direction preference (as has been discussed in the old manuscript),
while the non-bonded estimate requires the uniformity
of the density distribution and the isotropicity of the system.
Otherwise the cost of the error estimate would be $\mathcal O(N^2\log N)$.
In example 3, a global RDF is not well defined,
so we calculated the RDF and nearest neighbor approximation
only for the liquid phase, see the dotted line in Fig.7. By adding
the non-bonded correlation, the quality of the error estimate
is further improved.
Also the convergence with respect to
the neighboring range $R_g$ is investigated, see Fig.8.
Relevant changes to the manuscript
have been made on page 9,
11 (4-th line from the bottom), 12, 29 (12-th line). All changes are marked 
in red for convenience.
\\

@@

In the revised manuscript,
we consider both of the two types of the correlations:
(1) the bonded correlation
that originates from the rigid H-O
bond and H-O-H angle within one molecule,
and (2) the
non-bonded correlation or the
intermolecular correlation that originates from
a complex coupling of various intermolecular interactions.
Estimates for the bonded correlation
have already been developed by the old manuscript,
while the non-bonded estimate
is newly added according to the reviewers' suggestion.
The nearest neighbors are defined by neighbors closer than
a neighboring range $R_g$ (i.e. the $r_c$ in the reviewer's comment).
The non-bonded nearest neighbor approximation 
is expressed in terms of the radial distribution
functions (RDFs), see the new Eq. (21) and (22).
Please note that
both the bonded and non-bonded nearest neighbor approximations
require some uniformity of the correlation in the system:
the bonded estimate requires the uniformity of the water
direction preference (as has been discussed in the old manuscript),
while the non-bonded estimate requires the uniformity
of the density distribution and the isotropicity of the system, which
are also the prerequisites for reducing $\rho^{(2)}$ to $g(r)$.
Otherwise the cost of the error estimate would be $\mathcal O(N^2\log N)$.
In example 3, a global RDF is not well defined (because the system is inhomogeneous),
so we calculated the RDF and nearest neighbor approximation
only for the liquid phase, see the dotted line in Fig.7. By adding
the non-bonded correlation, the quality of the error estimate
is further improved.
Also the convergence with respect to
the neighboring range $R_g$ is investigated, see Fig.8.
Relevant changes to the manuscript
have been made on page 9,
11 (4-th line from the bottom), 12, 29 (12-th line). All changes are marked 
in red for convenience.
\\
